Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-29 bbbq_article.tex
Clean up single-figure-per-panel LaTex, add boldface to paneled figures

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_conservation.png}
  \caption{
    The number of SNPs in TMHs as expected by chance (left bar) 
    and found in the dbSNP database (right bar).
    Percentages are added to show the relative conservation
    of SNPs in TMHs found.
  }
  \label{fig:conservation}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_conservation_per_spanner.png}
  \caption{
    The number of SNPs in TMHs as expected by chance (red bars) 
    and found in the dbSNP database (right bars), 
    after splitting the data into single- and multi-spanners.
    Percentages are added to show the relative conservation
    of SNPs in TMHs found.
  }
  \label{fig:conservation_per_spanner}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected.png}
  \caption{
    Percentage of SNPs found in TMHs.
    Each point shows the predicted percentage of
    TMH (x-axis) and the observed occurrence of SNPs being located
    within a TMH (y-axis) for a protein.
    The dashed diagonal line shows the line of equality (i.e.
    equal conservation of TMHs and soluble protein regions).
    The blue line is a linear trend line that includes only the
    transmembrane proteins.
  }
  \label{fig:f_snps_found_and_expected}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation.png}
    \label{fig:conservation}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected.png}
    \label{fig:f_snps_found_and_expected}
  \end{subfigure}
  \caption{
      \textbf{(A)} 
      The number of SNPs in TMHs as expected by chance (left bar) 
      and found in the dbSNP database (right bar).
      Percentages are added to show the relative conservation
      of SNPs in TMHs found.
      \textbf{(B)}
      Percentage of SNPs found in TMHs.
      Each point shows the predicted percentage of
      TMH (x-axis) and the observed occurrence of SNPs being located
      within a TMH (y-axis) for a protein.
      The dashed diagonal line shows the line of equality (i.e.
      equal conservation of TMHs and soluble protein regions).
      The blue line is a linear trend line that includes only the
      transmembrane proteins.
  }
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation_per_spanner.png}
    \label{fig:conservation_per_spanner}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected_per_spanner.png}
    \label{fig:f_snps_found_and_expected_per_spanner}
  \end{subfigure}
  \caption{
      \textbf{(A)} 
      The number of SNPs in TMHs as expected by chance (red bars) 
      and found in the dbSNP database (right bars), 
      after splitting the data into single- and multi-spanners.
      Percentages are added to show the relative conservation
      of SNPs in TMHs found.
      \textbf{(B)} 
      Percentage of SNPs found in TMPs predicted to have only a single
      (left) or multiple (right) TMHs.
      The dashed diagonal lines show the expected line of equality 
      (i.e., equal conservation of TMHs and solvent-exposed 
      protein regions).
  }
\end{figure}
